Methodology for Assessing the State of the Practice for Domain X

### 2021-10-20 StateOfPractice/Methodology/Methodology.tex
Revisions to "How to Identify the Domain?" section

\begin{enumerate}
\item Identify the domain (X). (Section~\ref{SecIdentifyDomain})
\item Ask the Domain Expert to create a top ten list of software packages in the
  domain. (Section~\ref{SecDomainExpert})
\item Meet with the Domain Expert to brief them on the overall objective,
  research proposal, research questions, measurement template, and developer
  interviews. (Section~\ref{SecDomainExpert}) \label{StepMeeting}
\item Identify broad list of candidate software packages in the domain.
  (Section~\ref{SecIdentifyCandSoft})
\item Preliminary filter of software packages list.
  (Section~\ref{SecInitialFilter})
\item Review software list with Domain Expert. (Section~\ref{SecDomainExpert})
\item Domain Analysis (with the help of the Domain Expert).
(Section~\ref{SecDomainAnalysis})
\item Ask Domain Expert to vet domain analysis.
  (Section~\ref{SecDomainExpert})
\item Gather source code and documentation for each prospective software
  package.
\item Collect repository based information. (Section~\ref{SecEmpiricalMeasures})
\item Measure using measurement template. (Section~\ref{SecMeasureTemplate})
\item Survey developers (Section~\ref{SecSurveyQuestions})
\item Use AHP process to rank the software packages. (Section~\ref{SecAHP})
% \item Identify a short list of top software packages, typically four to six, for
%   deeper exploration according to the AHP rankings of the measurements.
\item Ask Domain Expert to vet AHP ranking. (Section~\ref{SecDomainExpert})
%\item Rank short list. (Section~\ref{SecRankShortList})
\item Answer research questions (from Section~\ref{SecResearchQuestions}) and
document answers.
\end{enumerate}

@@

A domain of research software must be identified. Research software is defined
in this exercise as ``software that is used to generate, process or analyze
results that [are intended] to appear in a publication'' \citep{hettrick2014uk}
in a scientific or engineering context.  Research software is a more general
term for what is often called scientific computing.  To be applicable for the
methodology described in this document, the chosen domain must have the
following properties:

\begin{enumerate}
\item The domain must have well-defined and stable theoretical underpinning.  A
  good sign of this is the existence of standard textbooks, preferably
  understandable by an upper year undergraduate student.
\item There must be a community of people studying the domain.
\item The software packages must have open source options.
\item A preliminary search, or discussion with experts, suggests that there will
  be numerous, at least 15, candidate software packages in the domain that
  qualify as `research software'.
\end{enumerate}

>>>>

\begin{enumerate}
\item Identify the domain (X). (Section~\ref{SecIdentifyDomain})
\item Ask the Domain Expert to create a top ten list of software packages in the
  domain. (Section~\ref{SecDomainExpert})
\item Meet with the Domain Expert to brief them on the overall objective,
  research proposal, research questions, measurement template, and developer
  interviews. (Section~\ref{SecDomainExpert}) \label{StepMeeting}
\item Identify the broad list of candidate software packages in the domain.
  (Section~\ref{SecIdentifyCandSoft})
\item Preliminary filter of software packages list.
  (Section~\ref{SecInitialFilter})
\item Review software list with Domain Expert. (Section~\ref{SecDomainExpert})
\item Domain Analysis (with the help of the Domain Expert).
(Section~\ref{SecDomainAnalysis})
\item Ask Domain Expert to vet domain analysis.
  (Section~\ref{SecDomainExpert})
\item Gather source code and documentation for each prospective software
  package.
\item Collect repository based information. (Section~\ref{SecEmpiricalMeasures})
\item Measure using measurement template. (Section~\ref{SecMeasureTemplate})
\item Survey developers. (Section~\ref{SecSurveyQuestions})
\item Use AHP process to rank the software packages. (Section~\ref{SecAHP})
% \item Identify a short list of top software packages, typically four to six, for
%   deeper exploration according to the AHP rankings of the measurements.
\item Ask Domain Expert to vet AHP ranking. (Section~\ref{SecDomainExpert})
%\item Rank short list. (Section~\ref{SecRankShortList})
\item Answer research questions (from Section~\ref{SecResearchQuestions}) and
document answers.
\end{enumerate}

@@

A domain of research software must be identified to begin the assessment.
Research software is defined in this exercise as ``software that is used to
generate, process or analyze results that [are intended] to appear in a
publication'' \citep{hettrick2014uk} in a scientific or engineering context.
Research software is a more general term for what is often called scientific
computing.  To be applicable for the methodology described in this document, the
chosen domain must have the following properties:

\begin{enumerate}
\item The domain must have well-defined and stable theoretical underpinning.  A
  good sign of this is the existence of standard textbooks, preferably
  understandable by an upper year undergraduate student.
\item There must be a community of people studying the domain.
\item The software packages must have open source options.
\item A preliminary search, or discussion with experts, suggests that there will
  be numerous, close to 30, candidate software packages in the domain that
  qualify as `research software'.
\end{enumerate}
